
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt]{article}
% This is a helpful package that puts math inside length specifications
\usepackage{calc}

% Layout: Puts the section titles on left side of page
\reversemarginpar

%% Letter sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1in,     % Length of section titles
            marginparsep=0.2in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}
\parskip=3pt

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactenum will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Allow urls to break across lines
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
		    
% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%PDF specific settings:
\usepackage[pdftex,
        pdftitle={curriculum vitae},
        pdfauthor={Jason Locklin},
        pdfproducer={pdfLaTeX}]{}

%Definitions (ie., \item[]) should start on a new, indented line
\usepackage{enumitem}
\setdescription{labelsep=\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[ -0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}


\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}% space between sections
		\pagebreak[3]
		\phantomsection\addcontentsline{toc}{section}{#1}%
         \nopagebreak \hspace{0in}% 
	 \nopagebreak
         \marginpar{
         \raggedright \scshape #1}#2}\nopagebreak

% An itemize-style list with lots of space between items
%\newenvironment{outerlist}[1][\enskip\textbullet]%
%        {\begin{enumerate}[#1]}{\end{enumerate}%
%         \vspace{-.6\baselineskip}}


\newlist{outerlist}{itemize}{3}
    \setlist[outerlist]{label=\enskip,leftmargin=*,itemsep=8pt}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactenum}[#1]}{\end{compactenum}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[1]}

% Support pandoc's "tightlist"
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% column width for contact info:
\newlength{\rcollength}\setlength{\rcollength}{2.5in}

% Include the content from markdown files with pandoc
% See makefile
\makeheading{Jason Locklin, Ph.D.}

\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
            & \\
                & \textit{e-mail:} \href{mailto:locklin.jason@gmail.com}{locklin.jason@gmail.com}\\
                & \textit{web:}
\href{https://jason.locklin.science}{jason.locklin.science}\\

\end{tabular}

\section{Profile Summary}\label{profile-summary}

Community research scientist with extensive applied experience in
healthcare and public education sectors. A high degree of technical
training and expertise regarding data collection, management and
advanced statistical analysis. Extensive experience working with
stakeholders and administration for program evaluation, knowledge
translation, and supporting organization goals and achievements.

\pagebreak[3]

\section{Education}\label{education}

\href{http://www.uwaterloo.ca/}{University of Waterloo}:

\begin{outerlist}
\tightlist
\item
  \href{http://psychology.uwaterloo.ca}{\textbf{Ph.D., Cognitive
  Neuroscience}} \hfill 2015

 \begin{innerlist}
  \tightlist
  \item
    \emph{Perceptual and Memory Deficits in Unilateral Neglect}
  \item
    Area of Study: Stroke, Perception, and Memory.
 \end{innerlist}
\item
  \href{http://psychology.uwaterloo.ca}{\textbf{M.A., Behavioural and
  Cognitive Neuroscience}} \hfill 2009

 \begin{innerlist}
  \tightlist
  \item
    \emph{Development of a Measure of Visuomotor Control for Assessing
    the Long-term Effects of Concussion}
  \item
    Area of Study: Fine Motor Control, Concussion Research.
 \end{innerlist}
\item
  \href{http://science.uwaterloo.ca}{\textbf{B.Sc. (Honours)}},
  Psychology, Biology (minor) \hfill 2007

 \begin{innerlist}
  \tightlist
  \item
    Course load including strong mix of Psychology with Natural and Life
    Sciences.
 \end{innerlist}
\end{outerlist}

\pagebreak[3]

\section{Professional Experience}\label{professional-experience}

\begin{outerlist}
\tightlist
\item
  \textbf{Research Officer},
  \href{https://www.wrdsb.ca/about-the-wrdsb/research/}{Waterloo Region
  District School Board} \hfill  2019 to Present

 \begin{innerlist}
  \tightlist
  \item
    Spearheaded the development and implementation of system-level
    measurements aligned with WRDSB's strategic goals, focusing on
    enhancing educational outcomes and operational efficiency through
    evidence-based practices.
  \item
    Collaborated with senior administrators and key stakeholders to
    provide actionable insights through comprehensive reports,
    facilitating data-driven decision-making to improve program
    effectiveness and student well-being.
  \item
    Managed and guided multiple research projects from conception
    through to completion, employing both quantitative and qualitative
    methodologies to assess and address complex educational challenges.
  \item
    Facilitated professional development workshops for WRDSB staff,
    focusing on the integration of research findings into practical
    teaching strategies and the development of a culture of continuous
    improvement and reflective practice.
  \item
    Responsible for a major, district-wide longitudinal student
    well-being research project that involves tens of thousands of
    students completing both a normed, standardized measurement and
    WRDSB developed questions that provide ongoing feedback to
    administration about school climate.
 \end{innerlist}
\item
  \textbf{Research Associate}, \href{https://family-medicine.ca/}{Centre
  for Family Medicine Family Health Team} \hfill 2016 - 2019

 \begin{innerlist}
  \tightlist
  \item
    Responsible for working as part of a multi-disciplinary team of
    researchers and healthcare professionals with a culture of inquiry
    and creative thinking, to develop, evaluate, and disseminate
    innovative primary-care programs to improve quality-of-care for
    persons with dementia, frailty, and related geriatric issues.
  \item
    Manage and achieve successful completion of an innovative pilot
    frailty screening measure for the Waterloo Region Local Health
    Network
  \item
    Develop a collaboration between a family health organization (family
    doctor's office) with a community pharmacy to deliver an empathetic
    screening program to all patients 75+ years old, using a
    human-centred approach.
  \item
    Field tested the screening measure with medical professionals and
    adjusted the screening measure for better strategy implementation
    (e.g., booking procedures were adjusted to better meet the needs of
    patients and administration)
  \item
    Utilized qualitative research methods to evaluate the successful
    improvements in confidence, self-report competence, and capacity of
    clinicians after participation in a memory-clinic training program.

   \begin{innerlist}
    \tightlist
    \item
      Trained and supervised undergraduate co-op students and volunteer
      research assistants.
   \end{innerlist}
 \end{innerlist}
\item
  \textbf{Statistical Consultant},
  \href{https://family-medicine.ca/}{Centre for Family Medicine Family
  Health Team} \hfill 2016

 \begin{innerlist}
  \tightlist
  \item
    Collected, tracked and made use of identity based data from clinical
    and administrative databases, outcome data, survey methodologies,
    and clinical measures for statistical analysis to evaluate new and
    existing procedures in primary care.
  \item
    Completed statistical reports with R, including data cleaning and
    validation, as well as visualization.
 \end{innerlist}
\end{outerlist}

\textbf{Graduate and Undergraduate Research,}
\href{http://psychology.uwaterloo.ca}{Department of Psychology},
\href{http://www.uwaterloo.ca/}{University of Waterloo}:

\begin{outerlist}
\tightlist
\item
  \textbf{Perception, action and brain injury:} Research Assistant.
  \hfill 2007 - 2015
\item
  Supervisor: Dr.~James Danckert

 \begin{innerlist}
  \tightlist
  \item
    Develop a motor-accuracy task for the measurement of concussion
    symptoms.
  \item
    Test neurological patients using a variety of neuropsychological
    tests and procedures, including Prism Adaptation.
  \item
    Develop and test a gaze-contingent task using real-time eye-tracking
    equipment.
 \end{innerlist}
\item
  \textbf{Decision making:} Research Assistant. \hfill             2007

 \begin{innerlist}
  \tightlist
  \item
    Supervisor: Dr.~Jon Fugelsang
  \item
    Develop web-based decision making experiments and collect data.
 \end{innerlist}
\item
  \textbf{Psychophysics.} Research Assistant. \hfill               2005
  - 2006

 \begin{innerlist}
  \tightlist
  \item
    Supervisor: Dr.~James Danckert
  \item
    Develop a computer-based task for a graduate student's project.
 \end{innerlist}
\item
  \textbf{Attention and clincal depression.} Laboratory Coordinator
  \hfill                 2005 - 2006

 \begin{innerlist}
  \tightlist
  \item
    Supervisor: Dr.~Scott McCabe
  \item
    Train research assistants, coordinate several covert-orienting
    experiments.
 \end{innerlist}
\item
  \textbf{Attention and clincal depression.} Research Assistant.
  (volunteer) \hfill                    2004 - 2005

 \begin{innerlist}
  \tightlist
  \item
    Supervisor: Dr.~Scott McCabe
  \item
    Conduct experimental psychology research experiments.
 \end{innerlist}
\end{outerlist}

\pagebreak[3]

\section{Professional
Affiliations}\label{professional-affiliations}

\begin{outerlist}
\tightlist
\item
  \textbf{Member}, \href{https://www.aero-aoce.org}{Association of
  Educational Researchers of Ontario} \hfill 2018 - 2024
\item
  \textbf{Member}, \href{http://thedaag.uwaterloo.ca/}{Danckert
  Attention and Action Group} \hfill 2008 - 2015
\item
  \textbf{Advisory Council}, \href{http://badsciencewatch.ca}{Bad
  Science Watch} \hfill 2012
\item
  \textbf{Member}, \href{VisionSciences.ca}{Vision Sciences Society}
  \hfill 2006
\end{outerlist}

\pagebreak[3]

\section{Service Activities}\label{service-activities}

\begin{outerlist}
\tightlist
\item
  \textbf{Executive Member at Large},
  \href{https://www.aero-aoce.org/aero-aoce-executiveexeacutecutif-drsquoaero-aoce.html}{Association
  of Educational Researchers of Ontario (AERO-AOCE)} \hfill 2023 -
  Present

 \begin{innerlist}
  \tightlist
  \item
    Serving as an executive member at large for AERO-AOCE, helping to
    drive the promotion and improvement of research, evaluation,
    planning, and development within Ontario's school systems.
  \item
    Contributing to initiatives that underscore the importance and
    impact of educational research in enhancing board of education
    strategies and outcomes.
 \end{innerlist}
\item
  \textbf{AERO-AOCE Fall Conference} on the Student Census, focusing on
  the analysis, reporting and community engagement phases of the project
  (\href{https://mail.google.com/mail/u/0/\#search/aero+fall+conference?projector=1}{Conference
  overview}) \hfill 2023

 \begin{innerlist}
  \tightlist
  \item
    Contributing organization and conference delivery and introduction
    of speakers.
 \end{innerlist}
\item
  \textbf{AERO-AOCE Spring Special Interest Group}; Climate Surveys:
  Student, Staff \& Parent.
  (\href{https://drive.google.com/file/d/1mNDOn_Xfc6B3_2UVLKF-4KWSdrHhBFQp/view}{Overview})
  \hfill 2023

 \begin{innerlist}
  \tightlist
  \item
    Contributing organization and program delivery, including MC role.
 \end{innerlist}
\item
  \textbf{Science Advisor}, Advisory Committee: Bad Science Watch.
  \hfill 2012

 \begin{innerlist}
  \tightlist
  \item
    Non-profit public interest advocacy group.
 \end{innerlist}
\item
  \textbf{President}: U.W. Undergraduate Psychology Society. \hfill 2005
  - 2007

 \begin{innerlist}
  \tightlist
  \item
    Student organization, administration of 8, over 600 members.
 \end{innerlist}
\end{outerlist}

\pagebreak[3]

\section{Funding and Awards}\label{funding-and-awards}

Grants

\begin{outerlist}
\tightlist
\item
  \textbf{\href{https://www.r-consortium.org/all-projects/r-user-group-support-program}{R-Consortium.org}}
  RUGS Program grant \hfill 2024

 \begin{innerlist}
  \tightlist
  \item
    Association of Education Researchers of Ontario R User Group funding
    grant for founding and delivering a summer workshop.
 \end{innerlist}
\item
  \textbf{\href{https://www.cfn-nce.ca/project/cat2018-19/}{Canadian
  Frailty Network}} Catalyst Grant Program \hfill 2018

 \begin{innerlist}
  \tightlist
  \item
    ``C5-75'': A primary care program to identify and support older
    adults living with frailty.\\
  \item
    Contributed to authoring successful grant application.
  \item
    Developed plan for collecting and analysing the data from the
    project.
  \item
    Project plan was to determine the most effective and valued aspects
    of the C5-75 program for identifying frailty in the community,
    guiding refinement and improving efficiency and applicability across
    primary care practice settings.
 \end{innerlist}
\end{outerlist}

Scholarships

\begin{description}
\tightlist
\item[\href{http://www.uwaterloo.ca}{Government of Ontario}]
Ontario Graduate Scholarship \hfill 2010--2011

Aiming for the Top Tuition Scholarship \hfill 2002--2003
\item[\href{http://www.uwaterloo.ca}{University of Waterloo}]
University of Waterloo Graduate Scholarship \hfill 2012

President's Graduate Scholarship \hfill 2010--2011

UW/Faculty of Arts Graduate Scholarship \hfill 2010

Psychology Memorial Fund Scholarship \hfill 2010

Arts Graduate Enhancement Scholarship \hfill 2009

University of Waterloo Merit Scholarship \hfill 2009

MERIT/Faculty of Arts Graduate Scholarship \hfill 2008--2009

Arts Grad Enhancement Scholarship \hfill 2007--2008
\end{description}

\pagebreak[3]

\section{Professional Development}\label{professional-development}

\begin{outerlist}
\tightlist
\item
  \textbf{\href{https://goanalyticsbi.com/workshops/}{Go Analytics};
  WRDSB Microsoft Power BI Hands-On Training} \hfill 2023

 \begin{innerlist}
  \tightlist
  \item
    Mastered the full spectrum of Power BI tools, from data connection
    to publishing dynamic dashboards.
  \item
    Learned from Microsoft Certified instructor Klayton Gonçalves,
    leveraging his extensive data analytics expertise.
  \item
    Gained proficiency in Power Query for data transformation and DAX
    for creating calculated columns and measures.
  \item
    Developed skills in building interactive visualizations and
    employing best practices for effective data presentation.
 \end{innerlist}
\item
  \textbf{\href{https://www.sickkids.ca/en/learning/our-programs/knowledge-translation-program/}{SickKids};
  The Scientist Knowledge Translation Training (SKTT™) course}
  \hfill 2018

 \begin{innerlist}
  \tightlist
  \item
    Completed intense 2-day workshop focused on effective research
    dissemination across fields like health, education, and social
    sciences.
  \item
    Learned from Dr.~Melanie Barwick, an expert in implementation
    science and knowledge translation, on enhancing research impact.
  \item
    Acquired strategies for making complex scientific information
    accessible to non-academic audiences.
  \item
    Developed skills in creating impactful knowledge translation plans
    tailored to diverse user groups.
 \end{innerlist}
\end{outerlist}

\href{http://www.uwaterloo.ca/}{University of Waterloo}, selected
examples follow:

\begin{outerlist}
\tightlist
\item
  \textbf{Technical}

 \begin{innerlist}
  \tightlist
  \item
    Multiple Regression (Psychology 632)
  \item
    Analysis of Variance (Psychology 630)
  \item
    Experimental Design (Statistics 830)
  \item
    Computer Vision (Systems Design Engineering 677)
  \item
    Data Analysis in Neuroscience (Biology 681)
 \end{innerlist}
\item
  \textbf{Non-technical}

 \begin{innerlist}
  \tightlist
  \item
    Visual Perception (Psychology 287)
  \item
    Neurobehavioral Analysis of Perceptual and Motor Deficits
    (Kinesiology 656)
  \item
    Nature \& Computational Correlations of Intelligence (Psychology
    670)
  \item
    Cognitive Neuropsychology I (Psychology 779A)
  \item
    Human Neuroanatomy and Neuropathology (Psychology 784)
 \end{innerlist}
\end{outerlist}

\pagebreak[3]

\section{Teaching}\label{teaching}

\href{http://psychology.uwaterloo.ca}{Department of Psychology},
\href{http://www.uwaterloo.ca/}{University of Waterloo}:

\begin{outerlist}
\tightlist
\item
  \textbf{Physiological Psychology}: T.A. \hfill    2011 \& 2014

 \begin{innerlist}
  \tightlist
  \item
    Provide weekly office hour extra instruction to students.
 \end{innerlist}
\item
  \textbf{Human Neuropsychology}: T.A. \hfill    2012

 \begin{innerlist}
  \tightlist
  \item
    Provide weekly office hour extra instruction to students.
 \end{innerlist}
\item
  \textbf{Res. in Human Cognitive Neuroscience}: T.A. \hfill    2010

 \begin{innerlist}
  \tightlist
  \item
    Provide assistance and feedback to students developing a research
    paper.
 \end{innerlist}
\item
  \textbf{Physiological Psychology}: T.A. \hfill    2009

 \begin{innerlist}
  \tightlist
  \item
    Provide weekly office hour extra instruction to students.
 \end{innerlist}
\item
  \textbf{Cognitive Processes}: T.A. \hfill    2008

 \begin{innerlist}
  \tightlist
  \item
    Provide extra instruction during office hours, grade term papers,
    give feedback to students.
 \end{innerlist}
\item
  \textbf{Basic Data Analysis}: T.A. \& Lab Instructor \hfill    2008

 \begin{innerlist}
  \tightlist
  \item
    Instruct a weekly tutorial for 30 students, consisting of a 30
    minute review lecture of the week's topic, and 30 minutes of
    practical instruction on solving data analytic problems.
  \item
    Develop weekly tutorial lesson plans in cooperation with other
    teaching assistants.
 \end{innerlist}
\item
  \textbf{Advanced Data Analysis}: T.A. \& Lab Instructor \hfill 2007

 \begin{innerlist}
  \tightlist
  \item
    Develop and lead regular 1 hour tutorials instructing 30 students to
    utilize the statistical software package SPSS in analyzing real
    world experimental and observational data.
 \end{innerlist}
\end{outerlist}

\pagebreak[3]

\section{Publications}\label{publications}

Refereed:

\begin{outerlist}
\item
  Lee, L., \textbf{Locklin, J.}, Patel, T., Lu, S. K., Hillier, L. M.
  (2022) Recruitment of participants for dementia research:
  interprofessional perspectives from primary care-based memory clinics.
  Neurodegenerative Disease Management. 12 (3), 117-127
  \href{https://doi.org/10.2217/nmt-2021-0053}{doi:10.2217/nmt-2021-0053}
\item
  Lee, L., Hillier, L., \textbf{Locklin, J.}, Lee, J., Slonim, K. (2019)
  Advanced care planning for persons with dementia in primary care:
  Attitudes and barriers among health-care professionals. Journal of
  palliative care, 34 (4), 248-254.
  \href{https://doi.org/10.1177/0825859718812463}{doi:10.1177/0825859718812463}
\item
  Lee, L., Hillier, L., \textbf{Locklin, J.}, Lumley-Leger, K., Molnar,
  F. (2019) Specialist and family physician collaboration: Insights from
  primary care-based memory clinics. Health \& Social Care in the
  Community. 27 (4), e522-e533.
  \href{https://doi.org/10.1111/hsc.12751}{doi:10.1111/hsc.12751}
\item
  Lee, L., Patel, T., \textbf{Locklin, J.}, Milligan., J., Pefanis, J.,
  Costa, A., Lee, J., Slonim, K., Giangregorio, L., Hunter, S., Keller,
  H., Boscart, V. (2018). Frailty screening and case-finding for complex
  chronic conditions in older adults in primary care. Geriatrics, 3 (3),
  39.
  \href{http://dx.doi.org/10.3390/geriatrics3030039}{doi:10.3390/geriatrics3030039}
\item
  \textbf{Locklin, J.} (2015). \emph{Perceptual and Memory Deficits in
  Unilateral Neglect.} (Dissertation, University of Waterloo, Waterloo,
  Canada).\\
  Retrieve from
  \href{http://hdl.handle.net/10012/9590}{hdl.handle.net/10012/9590}
\item
  \textbf{Locklin, J.}, Bunn, L., Roy, E. \& Danckert, J. (2010).
  Measuring Deficits in Visually Guided Action Post-Concussion.
  \emph{Sports Medicine}, \emph{40}, 183-187.\\
  \href{http://dx.doi.org/10.2165/11319440-000000000-00000}{doi:10.2165/11319440-000000000-00000}
\item
  \textbf{Locklin, J.} (2009). \emph{Development of a measure of
  visuomotor control for assessing the long-term effects of concussion.}
  (Master's thesis, University of Waterloo, Waterloo, Canada).\\
  Retrieve from
  \href{http://hdl.handle.net/10012/4740}{hdl.handle.net/10012/4740}
\item
  Striemer, C., \textbf{Locklin, J.}, Blangero, A., Rossetti, Y.,
  Pisella, L. \& Danckert, J. (2008). Attention for action? Examining
  the link between attention and visuomotor control deficits in a
  patient with optic ataxia. \emph{Neuropsychologia}, \emph{47},
  1491-1499.\\
  \href{http://dx.doi.org/10.1016/j.neuropsychologia.2008.12.021}{doi:10.1016/j.neuropsychologia.2008.12.021}
\end{outerlist}

Non-Refereed:

\begin{outerlist}
\item
  2022-2023 Safe, Caring and Inclusive School Survey -- Summary Report
  (2024). Public report produced by the Waterloo Region District School
  Board. Retrieve from
  \href{https://www.wrdsb.ca/about-the-wrdsb/research/reports/scis/2022-2023-safe-caring-and-inclusive-school-survey-summary-report/}{wrdsb.ca/about-the-wrdsb/research/reports/scis/2022-2023-safe-caring-and-inclusive-school-survey-summary-report/}
\item
  Newman, G., Duffy, C., Powell, A., Gray, R., \& \textbf{Locklin, J.}
  (2012). Position Paper on Electromagnetic Hypersensitivity (Idiopathic
  Environmental Intolerance Attributed to Electromagnetic Fields).
  Canada: \emph{Bad Science Watch}.\\
  Retrieve from
  \href{http://www.badsciencewatch.ca/projects/investigation-of-anti-wifi-activism-in-canada}{www.badsciencewatch.ca/projects/investigation-of-anti-wifi-activism-in-canada}
\item
  \textbf{Locklin, J.}, \& Danckert, J. (2010). Do we have Independent
  Visual Streams for Perception and Action? a Response. Preprint.\\
  Retrieve from \href{http://cogprints.org/6854/}{cogprints.org/6854/}
\item
  \textbf{Locklin, J.}, Danckert, J. (2009). Changes in Visuomotor
  Performance of Concussed Individuals. Poster. Abstract published in
  \emph{Journal of Vision}, \emph{9:8}, 1103-1103.\\
  \href{http://dx.doi.org/10.1167/9.8.1103}{doi:10.1167/9.8.1103}
\item
  Law, A., McCabe, S., \textbf{Locklin, J.}, Tan, C., \& Morris, S.
  (2006). Perceptions of social rank as a predictor of anger and
  depression symptoms. Poster presented at the Graduate Student Research
  Conference, University of Waterloo, Waterloo, Canada.

  \pagebreak[3]
\end{outerlist}

\section{Mathematical Expertise}\label{mathematical-expertise}

\begin{outerlist}
\tightlist
\item
  \textbf{Basic Statistics and Data Analysis}

 \begin{innerlist}
  \tightlist
  \item
    Hypothesis testing via means comparisons and correlations, including
    techniques for the prevention of elevated experiment-wise error.
  \item
    Data reduction and simplification using measures of central
    tendency, variance, and periodicity.
  \item
    Data visualization, including experience with the problem of
    communicating high-dimensional data on paper/screen.
  \item
    Experiment power and effect size calculations.
  \item
    Experimental design optimization.
 \end{innerlist}
\item
  \textbf{Advanced Statistics}

 \begin{innerlist}
  \tightlist
  \item
    Analysis of Variance and Covariance, as well as Logistic Regression
    (Generalized Linear Models).
  \item
    Multiple Regression, including model comparisons and variable coding
    for non-typical data sets.
  \item
    Bayesian hypothesis testing.
 \end{innerlist}
\end{outerlist}

\section{Technical Skills}\label{technical-skills}

\begin{outerlist}
\tightlist
\item
  \textbf{Statistical / Data Analytical Software}

 \begin{innerlist}
  \tightlist
  \item
    \href{http://www.r-project.org/}{R}, statistics programming, data
    visualization.
  \item
    \href{http://www.spss.com/}{SPSS}, statistical analysis for social
    sciences.
  \item
    \href{https://powerbi.microsoft.com/en-ca/}{Power BI}, Data
    modelling and dashboarding.
  \item
    \href{http://www.sas.com/}{SAS}, data management and advanced
    statistical analysis.
  \item
    \href{http://www.scipy.org/}{Scipy/Pylab}, Python library for
    scientific computation, data visualization.
  \item
    \href{https://www.mathworks.com/products/matlab/}{Matlab},
    high-level technical computing language.
 \end{innerlist}
\item
  \textbf{Laboratory Equipment and Software}

 \begin{innerlist}
  \tightlist
  \item
    \href{www.sr-research.com}{EyeLink II} host control (For controlling
    eye-tracking equipment).
  \item
    \href{http://www.psychopy.org/}{Psychopy}, Python library for
    building psychopysics and cognitive psychology experiments.
  \item
    Trained in lesion overlay analysis (Analysis of MRI brain imaging
    data)
  \item
    AcqKnowlege software in combination with BIOPAC laboratory equipment
    for physiological measurement (Electromyography (EMG) and Galvanic
    Skin Response (GSR))
  \item
    \href{http://www.pstnet.com/products/e-prime/}{E-Prime} for data
    collection in Psychology Research.
 \end{innerlist}
\item
  \textbf{Programming and Scripting Languages}

 \begin{innerlist}
  \tightlist
  \item
    Day-to-day familiarity with several scripting languages including
    Python, UNIX shell scripting (BASH).
  \item
    Experience using a variety of programming languages (C, Pascal, and
    Java).
  \item
    Experience using PHP with HTML and CSS in the development of
    web-based research experiments.
 \end{innerlist}
\item
  \textbf{Typesetting Software}

 \begin{innerlist}
  \tightlist
  \item
    Comfortable writing with TeX, LaTeX, and BibTeX for technical and
    scientific documents, as well as common office suites such as
    Microsoft Office and LibreOffice.
 \end{innerlist}
\end{outerlist}

\pagebreak[3]




\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
