
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt]{article}
% This is a helpful package that puts math inside length specifications
\usepackage{calc}

% Layout: Puts the section titles on left side of page
\reversemarginpar

%% Letter sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.0in,     % Length of section titles
            marginparsep=0in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}
\parskip=2pt

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactenum will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Allow urls to break across lines
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
		    
% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%PDF specific settings:
\usepackage[pdftex,
        pdftitle={curriculum vitae},
        pdfauthor={Jason Locklin},
        pdfproducer={pdfLaTeX}]{}

%Definitions (ie., \item[]) should start on a new, indented line
\usepackage{enumitem}
\setdescription{labelsep=\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[ -0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}


\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}% space between sections
		\pagebreak[3]
		\phantomsection\addcontentsline{toc}{section}{#1}%
         \nopagebreak \hspace{0in}% 
	 \nopagebreak
         \marginpar{
         \raggedright \scshape #1}#2}\nopagebreak

% An itemize-style list with lots of space between items
%\newenvironment{outerlist}[1][\enskip\textbullet]%
%        {\begin{enumerate}[#1]}{\end{enumerate}%
%         \vspace{-.6\baselineskip}}


\newlist{outerlist}{itemize}{3}
    \setlist[outerlist]{label=\enskip,leftmargin=*,itemsep=8pt}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]
    {\begin{samepage}\begin{compactenum}[#1]}
    {\end{compactenum}\end{samepage}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[1]}

% Support pandoc's "tightlist"
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% column width for contact info:
\newlength{\rcollength}\setlength{\rcollength}{3in}

% Include the content from markdown files with pandoc
% See makefile
\makeheading{Dr. Jason Locklin, Ph.D.}

\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
    & \\
  & Research Officer\\
  & Research and Organizational Transformation \\
  & Waterloo Region District School Board \\
  & 51 Ardelt Avenue, Kitchener ON, N2C 2R5 \\
  & \textit{Email:} \href{mailto:Jason@Locklin.science}{Jason@Locklin.science}\\

\end{tabular}

\subsection{Profile Summary}\label{profile-summary}

\textbf{Education Research Project Management and Organizational
Transformation}

Innovative community research with large-scale research projects and
skilled knowledge translation. Project management skills, complemented
with a high degree of technical expertise in research design, ethics
protocols, measurement theory, advanced qualitative and quantitative
statistical analysis, including the translation of complex data to
accessible and actionable insights to support and achieve organizational
goals.

\subsection{Education}\label{education}

\href{http://www.uwaterloo.ca/}{University of Waterloo}:

\begin{itemize}
\item
  \href{http://psychology.uwaterloo.ca}{\textbf{Ph.D., Psychology,
  Behavioural and Cognitive Neuroscience}} \hfill 2015

  \begin{itemize}
  \tightlist
  \item
    Dissertation: \emph{Perceptual and Memory Deficits in Unilateral
    Neglect}
  \item
    Area of Study: Stroke, Perception, and Memory.
  \end{itemize}
\end{itemize}

\pagebreak[2]

\begin{itemize}
\item
  \href{http://psychology.uwaterloo.ca}{\textbf{M.A., Psychology,
  Behavioural and Cognitive Neuroscience}} \hfill 2009

  \begin{itemize}
  \tightlist
  \item
    Thesis: \emph{Development of a Measure of Visuomotor Control for
    Assessing the Long-term Effects of Concussion}
  \item
    Area of Study: Fine Motor Control, Concussion Research.
  \end{itemize}
\end{itemize}

\pagebreak[2]

\begin{itemize}
\item
  \href{http://science.uwaterloo.ca}{\textbf{B.Sc. (Honours)}},
  Psychology, Biology (minor) \hfill 2007

  \begin{itemize}
  \tightlist
  \item
    Course load including strong mix of Psychology with Natural and Life
    Sciences.
  \end{itemize}
\end{itemize}

\pagebreak[3]

\subsection{Professional Experience}\label{professional-experience}

\begin{itemize}
\item
  \textbf{Research Officer},
  \href{https://www.wrdsb.ca/about-the-wrdsb/research/}{Waterloo Region
  District School Board} \hfill  2018 to Present

  \begin{itemize}
  \tightlist
  \item
    Lead development and implementation of system-level measurements to
    enhance educational outcomes and operational efficiency.
  \item
    Maintain and utilize a student demographic data tool to support
    equity goals and resource allocation.
  \item
    Collaborate with administrators to provide actionable data insights,
    improving program effectiveness and student well-being.
  \item
    Manage large research projects from conception to completion,
    employing quantitative and qualitative methods for data collection,
    analysis, and knowledge translation.
  \item
    Oversee a district-wide longitudinal student well-being research
    project, producing analytics and data visualizations with R.
  \item
    Conduct professional development workshops on integrating research
    data into school leadership strategies.
  \item
    Lead projects on student and staff well-being, from planning and
    data collection to communication of results.
  \end{itemize}
\end{itemize}

\pagebreak[2]

\begin{itemize}
\item
  \textbf{Research Associate}, \href{https://family-medicine.ca/}{Centre
  for Family Medicine} \hfill 2016 - 2018

  \begin{itemize}
  \tightlist
  \item
    Developed and evaluated primary-care programs for dementia and
    geriatric issues in a multidisciplinary team.
  \item
    Managed a pilot frailty screening measure and created a
    collaboration for screening patients 75+ years old.
  \item
    Refined screening measures based on field testing and evaluated
    clinician improvements in confidence and competence.
  \item
    Trained and supervised co-op students and volunteer research
    assistants.
  \end{itemize}
\end{itemize}

\pagebreak[2]

\begin{itemize}
\item
  \textbf{Statistical Consultant},
  \href{https://family-medicine.ca/}{Centre for Family Medicine}
  \hfill 2016

  \begin{itemize}
  \tightlist
  \item
    Analyzed identity-based and clinical data, including data cleaning
    and visualization with R, to evaluate primary care procedures.
  \end{itemize}
\end{itemize}

\pagebreak[2]

\textbf{Graduate and Undergraduate Research Employment},
\href{http://psychology.uwaterloo.ca}{Department of Psychology},
\href{http://www.uwaterloo.ca/}{University of Waterloo}:

\begin{itemize}
\tightlist
\item
  \textbf{Research Assistant}; Perception, action and brain injury.
  \hfill 2007 - 2015
\item
  \textbf{Research Assistant}; Decision making. \hfill             2007
\item
  \textbf{Research Assistant}; Psychophysics. \hfill               2005
  - 2006
\item
  \textbf{Laboratory Coordinator}; Attention and clinical depression.
  \hfill                 2005 - 2006
\item
  \textbf{Research Assistant}; Attention and clinical depression.
  (volunteer) \hfill                    2004 - 2005
\end{itemize}

\pagebreak[3]

\subsubsection{Affiliations}\label{affiliations}

\begin{itemize}
\tightlist
\item
  \textbf{Member}, \href{https://www.aero-aoce.org}{Association of
  Educational Researchers of Ontario} \hfill 2018 - 2024
\item
  \textbf{Member}, \href{http://thedaag.uwaterloo.ca/}{Danckert
  Attention and Action Group} \hfill 2008 - 2015
\item
  \textbf{Advisory Council}, \href{http://badsciencewatch.ca}{Bad
  Science Watch} \hfill 2012
\item
  \textbf{Member}, \href{VisionSciences.ca}{Vision Sciences Society}
  \hfill 2006
\end{itemize}

\pagebreak[3]

\subsection{Service Activities}\label{service-activities}

\begin{itemize}
\tightlist
\item
  \textbf{Executive Member at Large},
  \href{https://www.aero-aoce.org/aero-aoce-executiveexeacutecutif-drsquoaero-aoce.html}{Association
  of Educational Researchers of Ontario (AERO-AOCE)} \hfill 2023 -
  Present
\item
  \textbf{Host/Facilitator}, AERO-AOCE
  \href{https://mail.google.com/mail/u/0/\#search/aero+fall+conference?projector=1}{Fall
  Conference} \hfill 2023
\item
  \textbf{Host/Facilitator}, AERO-AOCE
  \href{https://drive.google.com/file/d/1mNDOn_Xfc6B3_2UVLKF-4KWSdrHhBFQp/view}{Spring
  Special Interest Group} \hfill 2023
\item
  \textbf{Science Advisor}, Advisory Committee: Bad Science Watch.
  \hfill 2012
\item
  \textbf{President}: U.W. Undergraduate Psychology Society. \hfill 2005
  - 2007
\end{itemize}

\pagebreak[3]

\section{Professional Development}\label{professional-development}

\begin{itemize}
\tightlist
\item
  \textbf{Project Management Professional (PMP) Certification};
  \href{https://www.pmi.org/certifications/project-management-pmp}{PMI}
  \hfill In-Progress
\item
  \textbf{Leading for Change: Understanding Colonialism, Human Rights
  and Equity}; \href{https://www.wrdsb.ca/}{WRDSB} \hfill 2024
\item
  \textbf{WRDSB Microsoft Power BI Hands-On Training};
  \href{https://goanalyticsbi.com/workshops/}{Go Analytics} \hfill 2023
\item
  \textbf{The Scientist Knowledge Translation Training (SKTT™) course};
  \href{https://www.sickkids.ca/en/learning/our-programs/knowledge-translation-program/}{SickKids}
  \hfill 2018
\end{itemize}

\pagebreak[3]

\subsection{Publications}\label{publications}

Refereed:

\begin{itemize}
\item
  Lee, L., \textbf{Locklin, J.}, Patel, T., Lu, S. K., Hillier, L. M.
  (2022) Recruitment of participants for dementia research:
  interprofessional perspectives from primary care-based memory clinics.
  Neurodegenerative Disease Management. 12 (3), 117-127
  \href{https://doi.org/10.2217/nmt-2021-0053}{doi:10.2217/nmt-2021-0053}
\item
  Lee, L., Hillier, L., \textbf{Locklin, J.}, Lee, J., Slonim, K. (2019)
  Advanced care planning for persons with dementia in primary care:
  Attitudes and barriers among health-care professionals. Journal of
  palliative care, 34 (4), 248-254.
  \href{https://doi.org/10.1177/0825859718812463}{doi:10.1177/0825859718812463}
\item
  Lee, L., Hillier, L., \textbf{Locklin, J.}, Lumley-Leger, K., Molnar,
  F. (2019) Specialist and family physician collaboration: Insights from
  primary care-based memory clinics. Health \& Social Care in the
  Community. 27 (4), e522-e533.
  \href{https://doi.org/10.1111/hsc.12751}{doi:10.1111/hsc.12751}
\item
  Lee, L., Patel, T., \textbf{Locklin, J.}, Milligan., J., Pefanis, J.,
  Costa, A., Lee, J., Slonim, K., Giangregorio, L., Hunter, S., Keller,
  H., Boscart, V. (2018). Frailty screening and case-finding for complex
  chronic conditions in older adults in primary care. Geriatrics, 3 (3),
  39.
  \href{http://dx.doi.org/10.3390/geriatrics3030039}{doi:10.3390/geriatrics3030039}
\item
  \textbf{Locklin, J.} (2015). \emph{Perceptual and Memory Deficits in
  Unilateral Neglect.} (Dissertation, University of Waterloo, Waterloo,
  Canada).\\
  Retrieve from
  \href{http://hdl.handle.net/10012/9590}{hdl.handle.net/10012/9590}
\item
  \textbf{Locklin, J.}, Bunn, L., Roy, E. \& Danckert, J. (2010).
  Measuring Deficits in Visually Guided Action Post-Concussion.
  \emph{Sports Medicine}, \emph{40}, 183-187.\\
  \href{http://dx.doi.org/10.2165/11319440-000000000-00000}{doi:10.2165/11319440-000000000-00000}
\item
  \textbf{Locklin, J.} (2009). \emph{Development of a measure of
  visuomotor control for assessing the long-term effects of concussion.}
  (Master's thesis, University of Waterloo, Waterloo, Canada).\\
  Retrieve from
  \href{http://hdl.handle.net/10012/4740}{hdl.handle.net/10012/4740}
\item
  Striemer, C., \textbf{Locklin, J.}, Blangero, A., Rossetti, Y.,
  Pisella, L. \& Danckert, J. (2008). Attention for action? Examining
  the link between attention and visuomotor control deficits in a
  patient with optic ataxia. \emph{Neuropsychologia}, \emph{47},
  1491-1499.\\
  \href{http://dx.doi.org/10.1016/j.neuropsychologia.2008.12.021}{doi:10.1016/j.neuropsychologia.2008.12.021}
\end{itemize}

Non-Refereed:

\begin{itemize}
\item
  2022-2023 Safe, Caring and Inclusive School Survey -- Summary Report
  (2024). Public report produced by the Waterloo Region District School
  Board. Retrieve from
  \href{https://www.wrdsb.ca/about-the-wrdsb/research/reports/scis/2022-2023-safe-caring-and-inclusive-school-survey-summary-report/}{wrdsb.ca/about-the-wrdsb/research/reports/scis/2022-2023-safe-caring-and-inclusive-school-survey-summary-report/}
\item
  Newman, G., Duffy, C., Powell, A., Gray, R., \& \textbf{Locklin, J.}
  (2012). Position Paper on Electromagnetic Hypersensitivity (Idiopathic
  Environmental Intolerance Attributed to Electromagnetic Fields).
  Canada: \emph{Bad Science Watch}.\\
  Retrieve from
  \href{http://www.badsciencewatch.ca/projects/investigation-of-anti-wifi-activism-in-canada}{www.badsciencewatch.ca/projects/investigation-of-anti-wifi-activism-in-canada}
\item
  \textbf{Locklin, J.}, \& Danckert, J. (2010). Do we have Independent
  Visual Streams for Perception and Action? a Response. Preprint.\\
  Retrieve from \href{http://cogprints.org/6854/}{cogprints.org/6854/}
\item
  \textbf{Locklin, J.}, Danckert, J. (2009). Changes in Visuomotor
  Performance of Concussed Individuals. Poster. Abstract published in
  \emph{Journal of Vision}, \emph{9:8}, 1103-1103.\\
  \href{http://dx.doi.org/10.1167/9.8.1103}{doi:10.1167/9.8.1103}
\item
  Law, A., McCabe, S., \textbf{Locklin, J.}, Tan, C., \& Morris, S.
  (2006). Perceptions of social rank as a predictor of anger and
  depression symptoms. Poster presented at the Graduate Student Research
  Conference, University of Waterloo, Waterloo, Canada.
\end{itemize}

\pagebreak[3]




\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
